Optimal (Multiway) Spatial Joins

### 2024-06-01 5.2.tex
5.2

\noindent \underline{\em Proof of Statement (1).} Consider any tuple $\bm{t} = (r_1,...,r_{k-3}, h', v) \in \J(R_1,...,R_{k-3},H',V)$. Let $h$ be the full segment of $h'$. Folloing our conventions, $B_\bm{t}$ denotes the intersection point of $h'$ and $v$, and it is covered by the rectangles $r_1,...,r_{k-3}$. As $h$ is the full segment of $h'$, $B_\bm{t} \in h$, and $B_\bm{t}$ is also the intersection of $h$ and $v$. Let $r_{k-2}$ be an arbitrary rectangle in $\contained_{R_{k-2}}(\bm{t})$. By the definition of $\contained_{R_{k-2}}(\bm{t})$, $r_{k-2}$ covers the effective segment of $h'$, whose right enpoint is $B_{\bm{t}}$. Therefore, $B_{\bm{t}}$ is covered by each of the rectangles $r_1,...,r_{k-2}$. Equivalently, $h \cap v \bigcap_{i = 1}^{k-2} r_i = B_\bm{t} \neq \emptyset$. Hence,
$\bm{t} \in \J(R_1,...,R_{k-2},H,V)$. To show that $\bm{t} \in \J_2$, we need to prove that $r_{k-2}$ covers the left endpoint of $h$. It is true because $r_{k-2}$ covers the effective segment of $h'$, whose left endpoint is the same as the left endpoint of $h$.

>>>>

\noindent \underline{\em Proof of Statement (1).} Consider any tuple $\bm{t} = (r_1,...,r_{k-3}, h', v) \in \J(R_1,...,R_{k-3},H',V)$. Let $h$ be the full segment of $h'$. Following our conventions, $B_\bm{t}$ denotes the intersection point of $h'$ and $v$, and it is covered by the rectangles $r_1,...,r_{k-3}$. As $h$ is the full segment of $h'$, $B_\bm{t} \in h$, and $B_\bm{t}$ is also the intersection of $h$ and $v$. Let $r_{k-2}$ be an arbitrary rectangle in $\contained_{R_{k-2}}(\bm{t})$. By the definition of $\contained_{R_{k-2}}(\bm{t})$, $r_{k-2}$ covers the effective segment of $h'$, whose right enpoint is $B_{\bm{t}}$. Therefore, $B_{\bm{t}}$ is covered by each of the rectangles $r_1,...,r_{k-2}$. Equivalently, $h \cap v \bigcap_{i = 1}^{k-2} r_i = B_\bm{t} \neq \emptyset$. Hence,
$\bm{t} \in \J(R_1,...,R_{k-2},H,V)$. To show that $\bm{t} \in \J_2$, we only need to prove that $r_{k-2}$ covers the left endpoint of $h$. It is true because $r_{k-2}$ covers the effective segment of $h'$, whose left endpoint is the same as the left endpoint of $h$.
